TBD

### 2019-02-06 inverse_problems/inverse_problems.tex
no message

@@

The models we described so far assume a well-separated support and a deterministic signal. This models can be extended to stochastic signals and the separation condition can be alleviated by assuming a Poisson process. 
We consider the following observation model. Let $X =\RL$ be a random vector drawn from some fixed distribution. We observe a random vector $Y\in\R^{N-L+1}$ generated as follows. Points are chosen in $\{1,\dots,N-L=1\}$ according to a Poisson process with parameter $\gamma N$. The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.

>>>>

\paragraph{The well-separated model with a random signal}
In this model, we let the signal $x\in\RL$ to be a random vector drawn from some fixed distribution. We observe a random vector $Y\in\R^{N-L+1}$. The difference from the previous models is that here in each non-zero element of $s$  a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$.
This model generalize the homogeneous and heterogeneous models; if the distribution is a Delta function that it coincides with the homogeneous model, and if it is a sum of Diracs then it is the heterogeneous model.
\TODO{We need to write the  separation condition clearly}.

@@

The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
We consider the following observation model. Let $X =\RL$ be a random vector drawn from some fixed distribution.
In this model, points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma N$. The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
